Finding Maximum $k$-Cliques Faster Using Lazy Global Domination

### 2016-05-17 paper/paper.tex
Less wordy

The key step in \citeauthor{Tomita:2010}'s algorithms is to produce a constructive colouring, which
is used in a clever way.  The $\colourOrder$ routine does not just return the number of colours
used. Instead, it returns a pair of arrays, $\order$ and $\bounds$. The $\order$ array contains
vertices, in the order in which they were coloured. The $i$th entry of the $\bounds$ array contains
the colour number used for the $i$th vertex in $\order$. We illustrate this in
\cref{figure:colours}. Crucially, $\bounds$ is non-decreasing (i.e.\ $\bounds[i+1] \ge \bounds[i]$),
and we may colour the subgraph induced by the first $i$ vertices of $\order$ using $\bounds[i]$
colours.

>>>>

The key step in \citeauthor{Tomita:2010}'s algorithms is to produce a constructive colouring---the
$\colourOrder$ routine does not just return the number of colours used. Instead, it returns a pair
of arrays, $\order$ and $\bounds$. The $\order$ array contains vertices, in the order in which they
were coloured. The $i$th entry of the $\bounds$ array contains the colour number used for the $i$th
vertex in $\order$. We illustrate this in \cref{figure:colours}. Crucially, $\bounds$ is
non-decreasing (i.e.\ $\bounds[i+1] \ge \bounds[i]$), and we may colour the subgraph induced by the
first $i$ vertices of $\order$ using $\bounds[i]$ colours.
